Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-14 robdml.tex
tex
svg

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Efficiently Enhancing Adversarial Robustness for Deep Metric Learning}

@@

\subsection{Hardness Manipulation}

@@

\subsection{Gradual Adversary}

@@

\subsection{Intra-Class Structure Constraint}

@@

% 1. possible combinations

@@

HM + different pgditer
CUB, 2 4 8 16 32

@@

\subsection{Effectiveness of GA}

\subsection{Effectiveness of ICS}

>>>>

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhancing Adversarial Robustness for Deep Metric Learning}

@@

\subsection{Hardness Manipulation}
\label{sec:31}

\begin{figure}
	\includegraphics[width=\columnwidth]{hmillust.pdf}
	\caption{Illustration of Hardness Manipulation.}
	\label{fig:hm}
\end{figure}

@@

Note, the design of HM is flexible, and not coupled with specific sampling
strategy.
%
In other words, any existing or future triplet sampling strategy can
be adopted in HM.

\subsection{Gradual Adversary}
\label{sec:32}

@@

\subsection{Intra-Class Structure Constraint}
\label{sec:33}

@@

\input{tab-hmeff.tex}
% 1. possible combinations

@@

HM + different pgditer
CUB, 2 4 8 16 32
\cref{tab:hmeff}

@@

\subsection{Effectiveness of GA and ICS}

Put together for easier comparison.
